%
% file: dedication.tex
% author: V?ctor Bre?a-Medina
% description: Contains the text for thesis dedication
%

\chapter*{Dedication and acknowledgements}
\begin{SingleSpace}
\initial{A}bout one and half years ago, I first enjoyed the charm of the computer vision in the course CV given by Ronald Poppe. About eight months ago, I decided to focus my thesis project in the computer vision domain and sought help from Ronald Poppe, I really appreciate him that he accepted my request despite he was already under full workload then. 

\paragraph{} 
In the processes of this thesis project, Ronald gave me many many helpful suggestions on the project goal definition and architecture designs. I can always get timely and detailed feedbacks from him, no matter in the weekly reports or for some other discussions about the problems occurred in the project. And the several iterations of revision and the very detailed and helpful critiques from Ronald helped me make the best out of this thesis.

\paragraph{}
And the Prof. Zhenzhong Chen in the Wuhan University also gave me many helpful suggestions at the beginning of this thesis project and instructed me to learn many necessary background knowledge. Without the help of Prof. Zhenzhong Chen providing the workstation with two Titan X GPU cards, I can not timely finish the project based on the deep learning model since the training processing ran very very slow on my own laptop. 

\paragraph{}
At last, I would like to thank my wife Jie Yu, my son Yizhi and my daughter Jingyu. Without the understanding and supporting of my wife, I can not fulfill my plan to return to university and learn the Artificial Intelligence. My wife undertook the most responsibilities of taking care the children during my studies which help me concentrate on my thesis project. And my lovely son and daughter are also the most important crutch for me to really finish my thesis. 

\paragraph{}

Utrecht, the Netherlands \\
June 23, 2017
\begin{flushright}
	{Deliang Wu}
\end{flushright}                
    
    
\end{SingleSpace}
\clearpage